---
graphics: yes
name: Douglas
surname: Fritz
pronouns: he/him
phone: +44 07933 053400
# phone: +1 314 941 7182
position: MD/PhD Student, University of Cambridge/NIH/University of Colorado
address: Cambridge, UK
profilepic: /Users/douglasfritz/Git/CV/img/me.jpg
www: ''
email: douglasafritz7@gmail.com
github: douglasfritz
linkedin: "douglas-fritz"
orcid: "0000-0001-8822-4639"
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 4F7942
output: vitae::hyndman
header-includes:
  - \definecolor{linkscolor}{HTML}{026dbb}
  - \usepackage{caption}
  - \usepackage{hyperref}
  - \usepackage{colortbl}
  - \usepackage{hanging}
  - \arrayrulecolor{white}
  - \usepackage{changepage}
  - \hypersetup{colorlinks=true, linkcolor=linkscolor, filecolor=linkscolor, urlcolor=linkscolor, urlbordercolor=linkscolor}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
library(gsheet)
library(gt)
library(flextable)
```

```{r pretty, include=FALSE}
baretable <- function(tbl, digits = 0,
                      include.colnames = FALSE, include.rownames = FALSE,
                      hline.after = NULL,
                      size = getOption("xtable.size", NULL),
                      add.to.row = getOption("xtable.add.to.row", NULL),
                      longtable = FALSE,
                      ...) {
  xtable::xtable(tbl, digits = digits, ...) |>
    print(
      include.colnames = include.colnames,
      include.rownames = include.rownames,
      hline.after = hline.after,
      comment = FALSE,
      tabular.environment = if_else(longtable, "longtable", "tabular"),
      floating = FALSE,
      size = size,
      add.to.row = add.to.row,
      sanitize.text.function = function(x) {
        x
      }
    )
}

# Return dollars in pretty manner.
# Similar to prettyNum but with $ sign and working for numbers greater than 1e7
dollars <- function(x) {
  out <- paste0("\\$", sprintf("%.0f", x))
  paste0(gsub(
    "^0+\\.", ".",
    unname(prettyNum(out, ",", preserve.width = "none", scientific = FALSE))
  ))
}
```


```{r previous bylines, eval = FALSE}
#I am broadly interested in the fields of maternal/fetal health, planetary health, emerging pathogens, AI, infectious disease, virology and immunology. I'm a tinkerer: from latte machines, to laser cutters, to LLMs, I like fixing stuff, building stuff, and making my life better though STEAM.

```

# Education
\vspace*{-\baselineskip}
```{r education}
#Use the direct link to each sheet, otherwise need sheet id
gsheet2tbl("https://docs.google.com/spreadsheets/d/1e9C-H-qXmPScZwefxmjSOm8jpEeYP-c5dVqJIZrHnTQ/edit#gid=1760172285") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what = Degree,
                          when = Year,
                          where = Institution, 
                          with = Location, 
                          why,
                          .protect = FALSE) # Setting protect to FALSE allows line breaks
```

# Professional Appointments
\vspace*{-\baselineskip}
```{r work CV}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1e9C-H-qXmPScZwefxmjSOm8jpEeYP-c5dVqJIZrHnTQ/edit#gid=1554751840") %>%
tidyr::fill(-why) %>%
  vitae::detailed_entries(what = title,
                          when = date,
                          where = institution,
                          why = why,
                          .protect = F)

```

```{r work resume, eval=FALSE, include=FALSE}
#Resume Format with bullet points
#this part doesn't work very well, not currently run

gsheet2tbl("https://docs.google.com/spreadsheets/d/1e9C-H-qXmPScZwefxmjSOm8jpEeYP-c5dVqJIZrHnTQ/edit#gid=161085706") %>%
tidyr::fill() %>%
  vitae::detailed_entries(what = title,
                          when = date,
                          where = institution,
                          why,
                          .protect = F) 

```


# Selected Publications

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

```{r publication, results='asis'}
rbind(
  ##Journal Articles Sheet
    gsheet2tbl("https://docs.google.com/spreadsheets/d/1e9C-H-qXmPScZwefxmjSOm8jpEeYP-c5dVqJIZrHnTQ/edit#gid=0") %>%
  #filter(category == "peer-reviewed") %>%
    select(year, markdown),
  
# ##Technical Reports Sheet
#   gsheet2tbl("https://docs.google.com/spreadsheets/d/1e9C-H-qXmPScZwefxmjSOm8jpEeYP-c5dVqJIZrHnTQ/edit#gid=1473597883") %>%
#   #Selects the first 3 rows of technical reports
#   #slice(1:3) %>%
#   select(year, markdown)
#   #,

## Preprints Sheet
  gsheet2tbl("https://docs.google.com/spreadsheets/d/1e9C-H-qXmPScZwefxmjSOm8jpEeYP-c5dVqJIZrHnTQ/edit#gid=1558956454") %>%
    # Selects the first 3 rows of preprints
    # slice(1:3) %>%
    select(year, markdown)

  
) %>%
  arrange(-year) %>%
  select(markdown) %>%
  mutate(markdown = str_replace_all(markdown, "\\{|\\}", ""),
         markdown = str_replace_all(markdown, "Fritz, D.", "**Fritz, D.**")) %>%
  
# ##The resulting dataset is further sliced to select specific rows using slice.
    slice(1,2, 3, 5) %>%
  
  mutate(markdown = gsub("(https:[^ ]+)", "\\\\url{\\1}", markdown)) %>%
  pull(markdown) -> intl
  cat(paste(intl,nsep = " "), sep = '\n\n')

```
\endgroup
\leavevmode\newline

# Selected Presentations

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
```{r conference, results='asis'}
  ##Conference Sheet
    gsheet2tbl("https://docs.google.com/spreadsheets/d/1e9C-H-qXmPScZwefxmjSOm8jpEeYP-c5dVqJIZrHnTQ/edit#gid=318960497") %>%
  filter(year >= "2019" & Include != "N") %>%
    select(year, markdown)%>%
  arrange(-year) %>%
  select(markdown) %>%
  mutate(markdown = str_replace_all(markdown, "\\{|\\}", ""),
         markdown = str_replace_all(markdown, "Fritz, D.", "**Fritz, D.**")) %>%
  
  # slice(1,2, 3, 5) %>%
  
  pull(markdown) -> conf
  cat(paste(conf,nsep = " "), sep = '\n\n')

``` 
\endgroup
\leavevmode\newline

# Software
\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
```{r software, results='asis'}
#Software Sheet
gsheet2tbl("https://docs.google.com/spreadsheets/d/1e9C-H-qXmPScZwefxmjSOm8jpEeYP-c5dVqJIZrHnTQ/edit#gid=1692561333") %>%
  select(markdown) %>%
  mutate(markdown = str_replace_all(markdown, "\\{|\\}", ""),
         markdown = str_replace_all(markdown, "Fritz, D.", "**Fritz, D.**")) %>%
  pull(markdown) -> software
  cat(paste(software), sep = '\n\n')

```


\endgroup
\leavevmode\newline

# Fellowships

  * Physicians for Social Responsibility National's Next Generation Climate & Health Ambassador (2022)
  * Fulbright Fellow, North Macedonia (2019).

  
# Grants
\begingroup
\vspace*{-\baselineskip}
```{r grants}
#Resume Format with bullet points

gsheet2tbl("https://docs.google.com/spreadsheets/d/1e9C-H-qXmPScZwefxmjSOm8jpEeYP-c5dVqJIZrHnTQ/edit#gid=1320047315") %>%
tidyr::fill() %>%
  vitae::detailed_entries(what = award_name,
                          when = date,
                          where = organization,
                          why = details,
                          .protect = F)

```

# Skills
\vspace*{-2\baselineskip}
```{r skills, message=FALSE, warning=FALSE, results='asis'}
# Skills Sheet
skills_table <- gsheet2tbl("https://docs.google.com/spreadsheets/d/1e9C-H-qXmPScZwefxmjSOm8jpEeYP-c5dVqJIZrHnTQ/edit#gid=885656894") %>%
  mutate(category = ifelse(is.na(category), "", category),
         details = ifelse(is.na(details), "", details
         ))

# Render the table using kableExtra
kableExtra::kbl(skills_table, col.names = NULL, align=c("l","l"), escape = F) %>%
  kableExtra::column_spec(column = 1, bold = TRUE) %>%
  kableExtra::row_spec(row = 2, extra_latex_after = "\\arrayrulecolor{white}")
  


```
\endgroup
\leavevmode\newline
  
# Awards & Honors 
```{r awards, message=FALSE, warning=FALSE, results='asis'}

# Awards Sheet
gsheet2tbl("https://docs.google.com/spreadsheets/d/1e9C-H-qXmPScZwefxmjSOm8jpEeYP-c5dVqJIZrHnTQ/edit#gid=1898241161") %>%
 filter(year >= "2020") %>%
    select(year, award_name) %>%
  arrange(-year) %>% 
  baretable()
  
# # Alternative vitae format like edcuation:
# gsheet2tbl("https://docs.google.com/spreadsheets/d/1e9C-H-qXmPScZwefxmjSOm8jpEeYP-c5dVqJIZrHnTQ/edit#gid=1898241161") %>%
#   vitae::detailed_entries(what = award_name,
#                           when = year,
#                           where = organization,
#                           .protect = FALSE) %>% arrange(-year) %>%
#   filter(when >= "2020")


```


# Society Memberships

\begingroup
```{r memberships, results='asis'}
#results 'asis' is key to making this work with the latex style

gsheet2tbl("https://docs.google.com/spreadsheets/d/1e9C-H-qXmPScZwefxmjSOm8jpEeYP-c5dVqJIZrHnTQ/edit#gid=1398743395") %>%
select(organization) %>%
  pull(organization) -> societies
  cat(paste(societies,nsep = " "), sep = ", ")

```
\endgroup
\leavevmode\newline 

# University Leadership
\vspace*{-\baselineskip}
```{r unileadership, results='asis'}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1e9C-H-qXmPScZwefxmjSOm8jpEeYP-c5dVqJIZrHnTQ/edit#gid=1205009221") %>%
 filter(year_ended >= "2021") %>% 
  filter(type == "university") %>%
  arrange(desc(year_started), desc(year_ended)) %>%
brief_entries(
    what = title,
    when = date,
    with = organization
  )
```

# Community Leadership
\vspace*{-\baselineskip}
```{r comleadership, results='asis'}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1e9C-H-qXmPScZwefxmjSOm8jpEeYP-c5dVqJIZrHnTQ/edit#gid=1205009221") %>%
 filter(year_ended >= "2021") %>% 
  filter(type != "university") %>%
  arrange(desc(year_started), desc(year_ended)) %>%
brief_entries(
    what = title,
    when = date,
    with = organization
  )
```
# Current Projects

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
```{r current projects, results='asis'}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1e9C-H-qXmPScZwefxmjSOm8jpEeYP-c5dVqJIZrHnTQ/edit#gid=527060978") %>%
tidyr::fill(-date) %>%
  vitae::detailed_entries(
                          what = title,
                          with = institution_with,
                          where = why,
                          .protect = F)




```
\endgroup



# In The Media
```{r media, message=FALSE, warning=FALSE, results='asis'}

# Media Sheet
gsheet2tbl("https://docs.google.com/spreadsheets/d/1e9C-H-qXmPScZwefxmjSOm8jpEeYP-c5dVqJIZrHnTQ/edit#gid=957986345") %>%
 filter(year >= "2019" & !type %in% c("Univ. News", "Blog", "Profile", "Trade News", "Video")) %>%
    select(title, year, details_why_url) %>%
  arrange(-year) %>% 
  baretable()

```

# Notes

This CV is reproducible. All the source code behind this CV is available on \href{https://github.com/douglasfritz/CV}{my Github repo}.
